NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-05-31 Manuscript/manuscriptPS.tex
Update Lipid17 results

Molecular dynamics simulation data was collected with Open Collaboration method.
The simulated systems are listed in Table \ref{IONsystems}.
The simulation details are in SI or in references in the table.

@@

>>>>

Molecular dynamics simulation data was collected using
the Open Collaboration method \cite{botan15}.
The NMRlipids project blog (\url{nmrlipids.blogspot.fi}) and
the GitHub repository (\url{github.com/NMRLipids/NMRlipidsIVotherHGs})
were used as the communication platforms.
The simulated systems are listed in Table \ref{IONsystems} and
simulation details are given in the SI.
The simulation data is also indexed in the
searchable database (\url{nmrlipids.fi}),
and in the NMRlipids/MATCH GitHub repository (\url{https://github.com/NMRLipids/MATCH}).  

@@

The C-H bond order parameters were calculated directly
from the definition
\begin{equation}
S_{\rm CH}=\frac{1}{2}\langle 3\cos^2\theta -1 \rangle,
\end{equation}
where $\theta$ is the angle between the C-H bond and the membrane normal.
Angular brackets point to the average over all sampled configurations.
\todo{Error estimation should be discussed.}\\
The number density profiles were calculated using {\it gmx density} tool
from Gromacs sofware package \cite{gromacsMANUAL}.
